Storm surge modelling in the Strait of Georgia

### 2014-10-02 RoughWork/manuscript.tex
Edited captions

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/tides.pdf}
\caption{Evaluation of model tidal amplitude and phases for the M$_2$ and K$_1$ constituents. }
\label{fig:tides}
\end{figure}

@@

\section{Storm Surge Hindcasts}\label{sec:storm}
%outline: 
%1. factors contributing to storm surge with focus on Feb 2006 event
%2. Strong wind event but no surge (maybe Dec 2006 or Nov 2009)
%3. High resolution wind (hopefully Dec 2012)
A series of storm surge hindcasts is presented next. Storm surge simulations were started from rest at least three days prior to the event of interest to allow for adjustment of model currents. Stratification conditions from model spin-up at a time close to the event (within 5 days) were chosen to initialize the temperature and salinity fields. Boundary conditions include atmospheric forcing and fresh water input from rivers at the surface, sea surface height anomaly from observations at the open boundary, and tidal forcing with eight tidal constituents. Forcing the model with only eight tidal constituents leads to an error in modelled sea surface height predictions due to the omission of the next leading order tidal constituents such as J$_1$. Comparisons between full tidal predictions and tidal predictions using eight constituents suggest that this error can be up to 40 cm (check) during times of high tidal range, and in particular, during the storm surge season Nov-Feb. As such, storm surge model predictions were corrected by accounting for this error. Additionally, since the sea surface height is calculated about a zero reverence level, the modelled water level is determined by adding a long term average of mean sea level at the specified location to the modelled sea surface height and removing a background anomaly caused by topographic pressure gradients since the atmospheric reforecasting model uses a terrain following coordinate system. (Nancy: I think we need a better way of adjusting come publication time).

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for three simulations: A simulation with all forcing (blue), a simulation without atmospheric forcing (green), and a simulation without the sea surface height anomaly (red). }
\label{fig:factors}
\end{figure}
%not sure about the colours, but different line styles is really hard to make out.

%Finally, an assessment of the importance of including tide-surge interactions is presented next. A simulation of the surge propagation without including any tidal forcing is compared with the modelled residual in Figure \ref{fig:tidesurge}. Recall, the modelled residual is defined as the difference between the sea surface height in a simulation with all forcing and a simulation with tides and rivers only. A comparison between the modelled residual and a surge only run can determine the significance of the tide-surge interaction. This figure shows there is almost no difference between the simulations at all locations, rendering the tide-sure interaction negligible. In operational settings, running a surge only simulation and adding the predicted tides a posteriori could be more computationally efficient with only a small decrease in the accuracy of the prediction. 
% I'm not sure if removing a background state is really appropriate here. There could be some differences in the background states because of the tides(ie where fresh water moves to, etc). I also think it is more appropriate to use the atmospheric pressure to remove the background state...

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_tidesurge.pdf}
\caption{Modelled residuals (solid) compared a simulation of the surge propagation without tidal forcing (dashed). A background state has not been removed from these plots. }
\label{fig:tidesurge}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/tides.pdf}
\caption{Evaluation of model tidal amplitude and phases for the M$_2$ and K$_1$ constituents. On the left, a transect through the stations used for comparison. On the right, modelled M$_2$ (black) and K$_1$ (gray) amplitude (top) and phase (middle) compared with observations in the dashed curves of the same colour. The bottom plot displays the M$_2$ and K_$1$ complex differences.  }
\label{fig:tides}
\end{figure}

@@

\section{Storm Surge Hindcasts}\label{sec:storm}
%outline: 
%1. factors contributing to storm surge with focus on Feb 2006 event
%2. Strong wind event but no surge (maybe Dec 2006 or Nov 2009)
%3. High resolution wind (hopefully Dec 2012)
A series of storm surge hindcasts is presented next. Storm surge simulations were started from rest at least three days prior to the event of interest to allow for adjustment of model currents. Stratification conditions from model spin-up at a time close to the event (within 5 days) were chosen to initialize the temperature and salinity fields. Boundary conditions include atmospheric forcing and fresh water input from rivers at the surface, sea surface height anomaly from observations at the open boundary, and tidal forcing with eight tidal constituents. Forcing the model with only eight tidal constituents leads to an error in modelled sea surface height predictions due to the omission of the next leading order tidal constituents such as J$_1$. Comparisons between full tidal predictions and tidal predictions using eight constituents suggest that this error can be up to 40 cm (check) during times of high tidal range, and in particular, during the storm surge season Nov-Feb. As such, storm surge model predictions were corrected by accounting for this error. Additionally, since the sea surface height is calculated about a zero reverence level, the modelled water level is determined by adding a long term average of mean sea level at the specified location to the modelled sea surface height.

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for three simulations: A simulation with all forcing (solid black), a simulation without atmospheric forcing (solid grey), a simulation without the sea surface height anomaly (dashed black) and a simulation with only wind forcing, ie no sea surface height anomaly or pressure (dashed grey). }
\label{fig:factors}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_tidesurge.pdf}
\caption{Modelled residuals (solid) compared with a simulation of the surge propagation without tidal forcing (dashed). }
\label{fig:tidesurge}
\end{figure}
